SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-29 2017-Xudong-SMT/ActaInformatica.tex
polishing

\abstract{Open pNets are formal models that can express the behaviour of open systems, either
	synchronous, asynchronous, or heterogeneous. They are endowed with a symbolic operational semantics in
	terms of open automata, which allows us to check properties of
	such systems in a compositional manner. 
	We present an algorithm computing these semantics,
	building predicates expressing the synchronisation conditions
	between the events of the pNet sub-systems. Checking such
	predicates requires symbolic reasoning about first order logics and application-specific data. We use the Z3 SMT engine to check
	satisfiability of the predicates.
	%As an industrial oriented use-case, %we use so-called ``architectures''
	%for BIP systems, that have been used in the framework of an ESA project and to specify the control software of a nanosatellite at the EPFL Space Engineering Center. 
%	We also present several use-cases, in particular, encoding a BIP architecture
%	extended with explicit data and computing its
%	open automaton semantics. This automaton may be used to prove
%	behavioural properties such as safety and liveness.
We also propose and implement an optimised
	algorithm that performs part of the pruning on-the-fly, and show 
	its correctness with respect to the original one.
	We illustrate the approach using two use-cases: the first one is a
	classical process-algebra operator for which we provide several
	encodings, and prove some basic properties. The second is  industry-oriented and based on the so-called ``BIP architectures'', which have
	been used to specify the
	control software of a nanosatellite at the EPFL Space Engineering
	Center. We use pNets to encode a BIP architecture
	extended with explicit data, compute its semantics and discuss its
	properties, and then show how our algorithms scale up, using a
	composition of two such architectures.}

@@

\ERIC{The set $L1$ may contain unreachable transitions, the last step of the
algorithm builds the final Open Automaton as a traversal of $L1$,
starting at the initial state $InitState(p)$ as defined in
page~\pageref{def-states}. More precisely, this is a residual
algorithm building a graph from transitions in $L1$, and states are
the set of target states of transitions in $L1$, plus the initial
states. Each state in the graph is decorated with a set of its local
variables, and a list of their possible assignments,
gathered during the traversal using the ``Post'' parts of the
OTs.}

\ERIC{A further reduction may now be gained by using the information from
these sets of possible assignments: adding this information when
checking satisfiability of transitions leaving a given state may
result in more Unsat transitions: the set of possible
assignments computed by the algorithm is an over approximation of
possible values of the 
variables of such state, so narrowing it means we get a better
approximation, and potentially more information, which can be used in
the SAT checking of subsequent transitions. In turn this may reduce the possible
assignments of the corresponding target states. In theory we should
iterate this procedure, each iteration reducing the set of
transitions, and the sets of assignments; the final Open Automaton
would be the fix point of this iteration. In practice this would be
expensive, and it is not incorrect to leave some Unsat OTs in the
result; in practical cases, very little will be gained computing the
fixpoint, so we only perform one step. Further algorithms 
(e.g. model-checking or equivalence checking) will be able to use the
full information from the predicates and the assignment sets.}

@@

%\begin{proof}
%  Let $pn=<...>$ be a pNet. The set of states 
%  managed by the two algorithms both are subsets of the cartesian
%  product of the pLTS states, as defined in \pageref{def-states}. In a
%  similar way, the set of state variables are also equal. Comparing
%  transitions requires a little more care, because within the
%  MakeTransitions function, fresh variables are created everytime a
%  synchronisation vector is used (this occurs within the $MkPred$ and
%  $matching$ functions). However, given a global state, the call of
%  $MakeTransitions$ will always returns exactly the same set of OTs, up to
%  renaming of these fresh variables\footnote{I think this does not
%    need any specific proof, given that it is the same function,
%    called with the same arguments}.
%
%  Let us define the following sets of OTs, as computed by the 2
%  algorithms:
%  \ERIC{not sure whether all these sets are useful, but it's good to
%    have them precisely defined for the moment}
%  \begin{itemize}
%    \item $L1$ = original set of transitions by Algorithm 1
%      (i.e. before line 11), 
%    \item $L1-sat$ = original set of transitions by Algorithm 1, after
%      satisfiability check (i.e. after line 11),
%    \item $L1-reach$ = final set of OTs of Algorithm 1, as computed
%      by line 12.
%    \item $L2-sat$ = original set of transitions by Algorithm 2
%      (i.e. before line 13), 
%    \item $L2-reach$ = final set of OTs of Algorithm 2, as computed
%          by line 13.
%  \end{itemize}
%
%  For each of these, define $States : OT^* -> State^*$ the function
%  computing the set of target states of a set of OTs.
%
%  We want to prove that $L1-reach = L2-reach$ (upto renaming of fresh
%  variables) and $States(L1-reach) = States(L2-reach)$.
%
%  From the structure of the main loops of the algorithms, we know that
%  $L1-sat \subset L2-sat$ and subsequently $States(L1-sat) \subset       
%  States(L2-sat)$.
%  \qed
%\end{proof}
%  
%    \medskip
%  \noteInEM{I keep below the original proof draft from Xudong, though
%    I'm not sure if parts of it can be reused}
\begin{proof of Theorem \ref{Th:CorrectnessWithoutAssignments}}

Let
 \begin{itemize}
    \item $L1$ = original set of transitions by Algorithm 1
      (i.e. before line 11), 
    \item $L1_{sat}$ = original set of transitions by Algorithm 1, after
      satisfiability check (i.e. after line 11),
    \item $L1_{reach}$ = final set of OTs of Algorithm 1, as computed
      by line 12.
    \item $L2_{sat}$ = original set of transitions by Algorithm 2
      (i.e. before line 13), 
    \item $L2_{reach}$ = final set of OTs of Algorithm 2, as computed
          by line 13.
\end{itemize}

For each of these, define $States: \langle OT\rangle\rightarrow\langle
State\rangle$ which is the function computing the set of states in a
set of OTs. Between two transitions sets of the algorithms, define
$Rename:  L1_{reach} \rightarrow L2_{reach}$ which is the function
renaming fresh variables.

@@

According to the definition of global states in
page~\pageref{def-states}, the global state
$\ostate{\tilde{s}}=\ostate{\tilde{s_0...s_n}}$ is a composition of n
pLTS states $s_{i}^{i\in [0,n]}$.

@@

  Suppose that  $\ostate{\tilde{t}}\in States(L2_{reach})$, it is reachable in the result automaton of Algorithm 2, so there exists a sequence of transitions $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where $Pred_j$ are all satisfiable. Then there exists the same state $\ostate{\tilde{t}}\in States(L1_{reach})$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t}}$ where $Pred_i$ are all satisfiable.
From the structure of the algorithms, 
\[\forall \ostate{\tilde{t}}\in States(L2_{reach}), OT = \ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}\in L2_{reach}\]
\[\exists OT' = \ostate{\tilde{t}}\xrightarrow{v'}\ostate{\tilde{t'}}\in L1 \quad s.t.\quad Rename(OT') = OT.\]
where $Pred$ and $Pred'$ are satisfiable.

@@

%Moreover,
Conversely,
\[\forall OT\notin L2_{reach}, \exists OT'\in L1, Rename(OT') = OT\]
where $Pred$ and $Pred'$ are not satisfiable. Then according to the pruning function in Algorithm 1, $OT'\notin L1_{reach}$.

As a result, we get that $L1_{reach}=L2_{reach}$, and subsequently, $States(L1_{reach})=States(L2_{reach})$.
%We will construct a mapping $f$: $State(L1-reach)\rightarrow
%State(L2-reach)$.
%\ERIC{I do not understand this, as states are identical. You would
%  rather need mapping betwen transitions ?}
%\begin{enumerate}
%\setlength{\itemindent}{3.5em}
%	\item[(Surjective)] If $\ostate{\tilde{s_0}}=Initial(p)$ then $f(\ostate{\tilde{s}})=\ostate{\tilde{t_0}}=Initial(p)$ must exists, the transitions started from them fulfill that
%	\[\forall \ostate{\tilde{t_0'}}, \ostate{\tilde{t_0}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}\in L_{Smart},\quad \exists\ostate{\tilde{s'}},\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}\in L.\]
%	The state $\ostate{\tilde{t'}}\in State(L_{Smart})$ and as $Pred_j$ of $\ostate{\tilde{t}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}$ is satisfiable, then if the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is also satisfiable, the state $\ostate{\tilde{s_0'}}$ is reachable in the original open automaton s.t. $\ostate{\tilde{s_0'}}\in State(L1)$, we can construct the mapping
%	\[f(\ostate{\tilde{s_0'}})=\ostate{\tilde{t_0'}}.\]
%	If the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s_0'}}\notin State(L1)$.
%	
%	Let $\textit{Explored}$, $\textit{Explored}_{Smart}$ respectively mean the explored states set of original algorithm and smart algorithm.
%	
%	Suppose that  $\ostate{\tilde{s}}\in \textit{Explored}$ there is $\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$ where $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$, there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$. 
%	
%	The transitions $\ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}$ and $\ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}$ have several cases:
%	\begin{enumerate}
%		\item[(1)] $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$
%		
%		We can find that 
%		 \[\exists\ostate{\tilde{s'}}\in \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}\quad where\quad f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
%		\item[(2)] $\ostate{\tilde{t'}}\notin \textit{Explored}_{Smart}$
%		
%		There must has 
%		\[\exists\ostate{\tilde{s'}}\notin \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}.\]
%		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is satisfiable then there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$. So the $\ostate{\tilde{s'}}$ is reachable in the original open automaton, we can construct the mapping
%		\[f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
%		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s'}}\notin State(L1)$.
%	\end{enumerate}	
%	Overall, \[\forall \ostate{\tilde{t}}\in State(L_{Smart}),\quad \exists\ostate{\tilde{s}}\in State(L1), f(\ostate{\tilde{s}})=\ostate{\tilde{t}}.\]
%	\item[(Injective)] If there is a pair of states $\ostate{\tilde{s}} and \ostate{\tilde{t}}$ constructs the mapping $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$. We can know that $\ostate{\tilde{s}}\in \textit{Explored},\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$.
%	
%	As when there is $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$, the state is must be $\ostate{\tilde{s'}}\in \textit{Explored}$ where $f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}$.
%	So it is a one-to-one mapping.
%\end{enumerate}
%
%Then as the function $f$ is both surjective and injective, it is a bijective function. The theorem is proved.
%
\end{proof}

@@

\TODO{Formalize the proof}
\begin{proof}
In Theorem 2, we have already proved the result automaton $OA_1$ and $OA_2$ of two algorithm are the same without the assignments.

@@

The structure implicitely computed by the algorithm (comprised in
the structure of an Open Automaton) is a triple $ Aut= \langle OTs, States, Assigns\rangle$.

Then the assignments set of $OA_1$ is $Assignments(L1, States(L1))$ and $OA_2$ is $Assignments(L2_{sat}, States(L2_{sat}))$. The computed triples are 
\[Aut_1 = \langle L1_{sat}, States(L1_{sat}), Assignments(L1, States(L1))\rangle\] and \[Aut_2 = \langle L2_{sat}, States(L2_{sat}), Assignments(L2_{sat}, States(L2_{sat}))\rangle\]

Based on the notation of the triple, define the function $Refine : Aut \rightarrow Aut$ refining the result automaton together with the assignments,
\begin{align*}
Refine(Aut) &=\langle OT', States(OT'), Assignments(OT', States(OT'))\rangle \\
&=Aut'
\end{align*}
where $OT' = OT - OT_{unsat}$, $OT_{unsat}$ is the set of transitions checked unsatisfiable in this iteration.

Given that every iteration will remove some unsatisfiable transitions, $Refine$ is a monotone function. There exists a sequence $Aut^n = Refine(Aut^{n-1})$ s.t. $|Aut^n|\le |Aut^{n-1}|$.
Let $Aut''$ contains the $OT''$ which has no more unsatisfiable transition, then there is $Aut'' = Refine(Aut'')$ and $|Aut''| = |Refine(Aut'')|$.

Let the fixed points $Refine(Aut''_1) = Aut''_1$, $Refine(Aut''_2) = Aut''_2$.

For the transitions set in $Aut''_1$ and $Aut''_2$, $L1''_{sat}=L1_{reach}$ and $L2''_{sat}=L2_{reach}$, we need to check their equivalence.
At the first iteration, the unsatisfiable transitions in $OA_1$ has only one case according to the relation between the assertions to check,
\begin{align*}
&\quad Pred\wedge \bigvee_i Assignments_i(L1, States(L1) \text{ is false}\\
&\quad\longrightarrow Pred\wedge \bigvee_j Assignments_j(L2_{sat}, States(L2_{sat})\text{ is false}\\
&\Rightarrow \forall t\in L1_{unsat} \longrightarrow t\in L2_{unsat}\\
&\Rightarrow L1_{unsat}\subseteq L2_{unsat}.
\end{align*}
However, its reverse direction is not fulfilled. Recall that $L1_{sat}=L2_{sat}$, these relations can imply that,
\begin{align*}
Assignments(L1, &States(L1))\supseteq Assignments(L2_{sat}, States(L2_{sat}))\\
&\supseteq Assignments(L1_{sat}-L1_{unsat}, States(L1_{sat}-L1_{unsat}))\\
&\supseteq Assignments(L2_{sat}-L2_{unsat}, States(L2_{sat}-L2_{unsat}))
\end{align*}
So after the first iteration, the unsatisfiable transitions in $OA_1$ has two cases,
\begin{align*}
&\forall t\in L1'_{unsat} \longrightarrow t\in L2'_{unsat}\\
\text{ or }&\forall t\in L1'_{unsat} \longrightarrow t\notin L2'_{sat}.
\end{align*}
By induction, after removing all the transitions not in the $L2''_{sat}$, we can get that $L1_{reach}=L2_{reach}$, subsequently, $States_{L1_{reach}}=States_{L2_{reach}}$,
$Assignments\\(L1_{reach},States_{L1_{reach}})=Assignments(L2_{reach},States_{L2_{reach}})$.
\end{proof}

@@

We validate the approach on two larger examples, 
based on a BIP architecture taken from an earlier nanosatellite case
study~\cite{CubETH-case-study}. We also show how such architectures
can be composed, and how our approach scales.
This example shows that
open-automata-based semantics can be instrumental in verifying the
properties enforced by the architectures through an encoding into open
pNets.
We also compare the practical performances of the 2 algorithms and
show the benefit gained using the smart approach.

>>>>

\abstract{Open pNets are formal models that can express the behaviour of open systems, either
	synchronous, asynchronous, or heterogeneous. They are endowed with a symbolic operational semantics in
	terms of open automata, which allows us to check properties of
	such systems in a compositional manner. 
	We present an algorithm computing these semantics,
	building predicates expressing the synchronisation conditions
	between the events of the pNet sub-systems. Checking such
	predicates requires symbolic reasoning about first order logics and application-specific data. We use the Z3 SMT engine to check
	satisfiability of the predicates.
	%As an industrial oriented use-case, %we use so-called ``architectures''
	%for BIP systems, that have been used in the framework of an ESA project and to specify the control software of a nanosatellite at the EPFL Space Engineering Center. 
%	We also present several use-cases, in particular, encoding a BIP architecture
%	extended with explicit data and computing its
%	open automaton semantics. This automaton may be used to prove
%	behavioural properties such as safety and liveness.
We also propose and implement an optimised
	algorithm that performs part of the pruning on-the-fly, and show 
	its correctness with respect to the original one.
	We illustrate the approach using two use-cases: the first one is a
	classical process-algebra operator for which we provide several
	encodings, and prove some basic properties. The second one is  industry-oriented and based on the so-called ``BIP architectures'', which have
	been used to specify the
	control software of a nanosatellite at the EPFL Space Engineering
	Center. We use pNets to encode a BIP architecture
	extended with explicit data, compute its semantics and discuss its
	properties, and then show how our algorithms scale up, using a
	composition of two such architectures.}

@@

\ERIC{The set $L1$ may contain unreachable transitions. To remove those transitions, the last step of the
algorithm builds the final open automaton via a traversal of $L1$,
starting at the initial state $InitState(p)$ as defined in
page~\pageref{def-states}. More precisely, this is a residual
algorithm building a graph from the reachable transitions in $L1$. 
%and states are the set of target states of the transitions. 
Each state in the graph is decorated with a set of its local
variables, and a list of their possible assignments,
gathered during the traversal using the ``Post'' parts of the
OTs.}

\ERIC{A further reduction may now be gained by using the information from
these sets of possible assignments: adding this information when
checking satisfiability of transitions leaving a given state may
result in more Unsat transitions. The set of possible
assignments computed by the algorithm is an over approximation of
possible values of the 
variables of such state, so narrowing it means we get a better
approximation, and potentially more information, which can be used in
the SAT checking of subsequent transitions. In turn, this may reduce the possible
assignments of the corresponding target states. In theory, we should
iterate this procedure, each iteration reducing the set of
transitions and the sets of assignments; the final open automaton
would be the fixed point of this iteration. In practice, this would be
expensive, and it is not incorrect to leave some Unsat OTs in the
result. From a  practical point of view, very little will be gained to compute the
fixed point, so we only perform one step of iteration. Further algorithms 
(e.g. model-checking or equivalence checking) will be able to use the
full information from the predicates and the assignment sets.}

@@

\begin{proof}
%  Let $pn=<...>$ be a pNet. The set of states 
%  managed by the two algorithms both are subsets of the cartesian
%  product of the pLTS states, as defined in \pageref{def-states}. In a
%  similar way, the set of state variables are also equal. Comparing
%  transitions requires a little more care, because within the
%  MakeTransitions function, fresh variables are created everytime a
%  synchronisation vector is used (this occurs within the $MkPred$ and
%  $matching$ functions). However, given a global state, the call of
%  $MakeTransitions$ will always returns exactly the same set of OTs, up to
%  renaming of these fresh variables\footnote{I think this does not
%    need any specific proof, given that it is the same function,
%    called with the same arguments}.
%
%  Let us define the following sets of OTs, as computed by the 2
%  algorithms:
%  \ERIC{not sure whether all these sets are useful, but it's good to
%    have them precisely defined for the moment}
%  \begin{itemize}
%    \item $L1$ = original set of transitions by Algorithm 1
%      (i.e. before line 11), 
%    \item $L1-sat$ = original set of transitions by Algorithm 1, after
%      satisfiability check (i.e. after line 11),
%    \item $L1-reach$ = final set of OTs of Algorithm 1, as computed
%      by line 12.
%    \item $L2-sat$ = original set of transitions by Algorithm 2
%      (i.e. before line 13), 
%    \item $L2-reach$ = final set of OTs of Algorithm 2, as computed
%          by line 13.
%  \end{itemize}
%
%  For each of these, define $States : OT^* -> State^*$ the function
%  computing the set of target states of a set of OTs.
%
%  We want to prove that $L1-reach = L2-reach$ (upto renaming of fresh
%  variables) and $States(L1-reach) = States(L2-reach)$.
%
%  From the structure of the main loops of the algorithms, we know that
%  $L1-sat \subset L2-sat$ and subsequently $States(L1-sat) \subset       
%  States(L2-sat)$.
%  \qed
%\end{proof}
%  
%    \medskip
%  \noteInEM{I keep below the original proof draft from Xudong, though
%    I'm not sure if parts of it can be reused}
\begin{proof of Theorem \ref{Th:CorrectnessWithoutAssignments}}

Let us first define some notations.
 \begin{itemize}
    \item $L1$: the original set of transitions by Algorithm 1
      (i.e. before line 11), 
    \item $L1_{sat}$:  the original set of transitions by Algorithm 1, after
      satisfiability check (i.e. after line 11),
    \item $L1_{reach}$: the final set of OTs of Algorithm 1, as computed
      by line 12.
    \item $L2_{sat}$: the original set of transitions by Algorithm 3
      (i.e. before line 13), 
    \item $L2_{reach}$: the final set of OTs of Algorithm 2, as computed
          by line 13.
\end{itemize}

For each of these, define $States: \langle OT\rangle\rightarrow\langle
State\rangle$ which is the function computing the set of states in a
set of OTs. Between two transition sets of the algorithms, define
$Rename:  L1_{reach} \rightarrow L2_{reach}$ which is the function
renaming fresh variables.

@@

According to the definition of global states in
page~\pageref{def-states}, the global state
$\ostate{\tilde{s}}=\ostate{\tilde{s_0...s_n}}$ is a composition of $n$
PLTS states $s_{i}^{i\in [0,n]}$.

@@

  Suppose that  $\ostate{\tilde{t}}\in States(L2_{reach})$. It is reachable in the result automaton of Algorithm 3, so there exists a sequence of transitions $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where $Pred_j$ are all satisfiable. Then there exists the same state $\ostate{\tilde{t}}\in States(L1_{reach})$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t}}$ where $Pred_i$ are all satisfiable.
From the structure of the algorithms, 
\[\forall \ostate{\tilde{t}}\in States(L2_{reach}), OT = \ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}\in L2_{reach}\]
\[\exists OT' = \ostate{\tilde{t}}\xrightarrow{v'}\ostate{\tilde{t'}}\in L1 \quad s.t.\quad Rename(OT') = OT.\]
where $Pred$ and $Pred'$ are satisfiable.

@@

%Moreover,
Conversely,
\[\forall OT\notin L2_{reach}, \exists OT'\in L1, Rename(OT') = OT\]
where $Pred$ and $Pred'$ are not satisfiable. Then according to the pruning function in Algorithm 1, $OT'\notin L1_{reach}$. 
As a result, we get that $L1_{reach}=L2_{reach}$, and subsequently, $States(L1_{reach})=States(L2_{reach})$.
%We will construct a mapping $f$: $State(L1-reach)\rightarrow
%State(L2-reach)$.
%\ERIC{I do not understand this, as states are identical. You would
%  rather need mapping betwen transitions ?}
%\begin{enumerate}
%\setlength{\itemindent}{3.5em}
%	\item[(Surjective)] If $\ostate{\tilde{s_0}}=Initial(p)$ then $f(\ostate{\tilde{s}})=\ostate{\tilde{t_0}}=Initial(p)$ must exists, the transitions started from them fulfill that
%	\[\forall \ostate{\tilde{t_0'}}, \ostate{\tilde{t_0}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}\in L_{Smart},\quad \exists\ostate{\tilde{s'}},\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}\in L.\]
%	The state $\ostate{\tilde{t'}}\in State(L_{Smart})$ and as $Pred_j$ of $\ostate{\tilde{t}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}$ is satisfiable, then if the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is also satisfiable, the state $\ostate{\tilde{s_0'}}$ is reachable in the original open automaton s.t. $\ostate{\tilde{s_0'}}\in State(L1)$, we can construct the mapping
%	\[f(\ostate{\tilde{s_0'}})=\ostate{\tilde{t_0'}}.\]
%	If the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s_0'}}\notin State(L1)$.
%	
%	Let $\textit{Explored}$, $\textit{Explored}_{Smart}$ respectively mean the explored states set of original algorithm and smart algorithm.
%	
%	Suppose that  $\ostate{\tilde{s}}\in \textit{Explored}$ there is $\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$ where $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$, there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$. 
%	
%	The transitions $\ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}$ and $\ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}$ have several cases:
%	\begin{enumerate}
%		\item[(1)] $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$
%		
%		We can find that 
%		 \[\exists\ostate{\tilde{s'}}\in \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}\quad where\quad f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
%		\item[(2)] $\ostate{\tilde{t'}}\notin \textit{Explored}_{Smart}$
%		
%		There must has 
%		\[\exists\ostate{\tilde{s'}}\notin \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}.\]
%		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is satisfiable then there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$. So the $\ostate{\tilde{s'}}$ is reachable in the original open automaton, we can construct the mapping
%		\[f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
%		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s'}}\notin State(L1)$.
%	\end{enumerate}	
%	Overall, \[\forall \ostate{\tilde{t}}\in State(L_{Smart}),\quad \exists\ostate{\tilde{s}}\in State(L1), f(\ostate{\tilde{s}})=\ostate{\tilde{t}}.\]
%	\item[(Injective)] If there is a pair of states $\ostate{\tilde{s}} and \ostate{\tilde{t}}$ constructs the mapping $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$. We can know that $\ostate{\tilde{s}}\in \textit{Explored},\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$.
%	
%	As when there is $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$, the state is must be $\ostate{\tilde{s'}}\in \textit{Explored}$ where $f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}$.
%	So it is a one-to-one mapping.
%\end{enumerate}
%
%Then as the function $f$ is both surjective and injective, it is a bijective function. The theorem is proved.
%
\hfill\qed
\end{proof}

@@

\TODO{Formalize the proof}
\begin{proof}
In Theorem 2, we have already proved the result automata $OA_1$ and $OA_2$ of the two algorithm are the same without the assignments.

@@

The structure implicitely computed by the algorithm is a triple $ Aut= \langle OTs, States, Assigns\rangle$.

Then the assignments set of $OA_1$ is $Assignments(L1, States(L1))$ and that of $OA_2$ is $Assignments(L2_{sat}, States(L2_{sat}))$. The computed triples are 
\[Aut_1 = \langle L1_{sat}, States(L1_{sat}), Assignments(L1, States(L1))\rangle\] and \[Aut_2 = \langle L2_{sat}, States(L2_{sat}), Assignments(L2_{sat}, States(L2_{sat}))\rangle \ . \]

Based on the notation of the triple, we define the function $Refine : Aut \rightarrow Aut$ refining the result automaton together with the assignments,
\begin{align*}
Refine(Aut) &=\langle OT', States(OT'), Assignments(OT', States(OT'))\rangle \\
&=Aut'
\end{align*}
where $OT' = OT - OT_{unsat}$, $OT_{unsat}$ is the set of transitions checked unsatisfiable in this iteration.

Given that every iteration will remove some unsatisfiable transitions, $Refine$ is a monotone function. There exists a sequence $Aut^n = Refine(Aut^{n-1})$ s.t. $|Aut^n| < |Aut^{n-1}|$.
Let $Aut''$ contains the $OT''$ which has no more unsatisfiable transition, then there is $Aut'' = Refine(Aut'')$ and $|Aut''| = |Refine(Aut'')|$.
Let $Aut''_1$ and $Aut''_2$ be the two
 fixed points with $Refine(Aut''_1) = Aut''_1$, $Refine(Aut''_2) = Aut''_2$.

For the transition sets in $Aut''_1$ and $Aut''_2$, $L1''_{sat}=L1_{reach}$ and $L2''_{sat}=L2_{reach}$, we need to check their equivalence.
At the first iteration, the unsatisfiable transitions in $OA_1$ has only one case according to the relation between the assertions to check,
\begin{align*}
&\quad Pred\wedge \bigvee_i Assignments_i(L1, States(L1) \text{ is false}\\
&\quad\longrightarrow Pred\wedge \bigvee_j Assignments_j(L2_{sat}, States(L2_{sat})\text{ is false}\\
&\Rightarrow \forall t\in L1_{unsat} \longrightarrow t\in L2_{unsat}\\
&\Rightarrow L1_{unsat}\subseteq L2_{unsat}.
\end{align*}
However, its reverse direction is not fulfilled. Recall that $L1_{sat}=L2_{sat}$, these relations can imply that,
\begin{align*}
Assignments(L1, &States(L1))\supseteq Assignments(L2_{sat}, States(L2_{sat}))\\
&\supseteq Assignments(L1_{sat}-L1_{unsat}, States(L1_{sat}-L1_{unsat}))\\
&\supseteq Assignments(L2_{sat}-L2_{unsat}, States(L2_{sat}-L2_{unsat}))
\end{align*}
So after the first iteration, the unsatisfiable transitions in $OA_1$ has two cases,
\begin{align*}
&\forall t\in L1'_{unsat} \longrightarrow t\in L2'_{unsat}\\
\text{ or }&\forall t\in L1'_{unsat} \longrightarrow t\notin L2'_{sat}.
\end{align*}
By induction, after removing all the transitions not in $L2''_{sat}$, we obtain  $L1_{reach}=L2_{reach}$, which implies that $States_{L1_{reach}}=States_{L2_{reach}}$ and
$$Assignments\\(L1_{reach},States_{L1_{reach}})=Assignments(L2_{reach},States_{L2_{reach}})\ .$$
\hfill\qed
\end{proof}

@@

We validate the approach on two larger examples, 
based on a BIP architecture taken from an earlier nanosatellite case
study~\cite{CubETH-case-study}. We also show how such architectures
can be composed, and how our approach scales.
This example shows that
open-automata-based semantics can be instrumental in verifying the
properties enforced by the architectures through an encoding into open
pNets.
We also compare the practical performances of the two algorithms and
show the benefit gained using the smart approach.
